\thesistitle

### 2019-08-17 sections/discussion.tex

>>>>

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R. In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1). Often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (34.7\% more cloned nodes for T2). The main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types. T3R and T3 only a little bit higher than T2R and T2.

### 2019-08-17 sections/results.tex

\chapter{Results}\label{ch:results}
In this chapter, we present the results of our experiments. All these results were obtained using CloneRefactor.

\section{Clone types}\label{sec:clonetypeexperiments}
In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Chapter \ref{chap:clonetypes}. When running our clone detection script over the corpus, we get the results displayed in Figure~\ref{fig:typeres}.

\begin{figure}[H]
  \centering
    \includegraphics[width=.5\columnwidth]{img/TypeResults}
      \caption{Number of cloned declarations/statements.}
  \label{fig:typeres}
\end{figure}

In this figure, the number of cloned nodes per clone type are displayed. The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (34.7\%) because the T2R definition is more strict. T3R and T3 are similar to T2R and T2 because our dataset does not have so many gapped clones for the thresholds used.

We also measured the duration of finding clones by the different clone types. Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types. The reason for this is further explained in Section~\ref{chap:challenge}.

@@

\subsection{Clone context}
% How many clones are there in certain contexts? Experiments for relation, location, and context.
To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).

\subsubsection{Relation}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).

@@

\subsubsection{Contents}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).

>>>>

\chapter{Results}\label{ch:results}
In this chapter, we present the results of our experiments. We perform exploratory experiments to map the differences between clone types, contexts and refactoring opportunities.

\section{Clone types}\label{sec:clonetypeexperiments}
In this section, we look into the differences between the different clone types that were introduced in Chapter \ref{chap:clonetypes}.

\subsection{Found nodes}
In this section, we display our results regarding the differences in found nodes between clone type 1-3~\cite{roy2007survey} and type 1R-3R. Figure~\ref{fig:typeres} shows the number of cloned nodes found over the entire corpus for the different clone types (the word ``Type'' is abbreviated as ``T''). For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between cloned fragments. For type 3 and 3R clones, we allow a gap of 20\% the clones surrounding it.

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/TypeResults}
    \caption{Number of cloned nodes.}
\label{fig:typeres}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/DurationChart}
    \caption{Duration in minutes of identifying clones for clone type definitions.}
  \label{fig:performance}
  \end{minipage}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=.5\columnwidth]{img/TypeResults}
      \caption{Number of cloned nodes.}
  \label{fig:typeres}
\end{figure}

\subsection{Performance}
We also measured the duration of finding clones by the different clone types. Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types. The reason for this is further explained in Section~\ref{chap:challenge}.

@@

\section{Clone context}
% How many clones are there in certain contexts? Experiments for relation, location, and context.
To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).

\subsection{Relation}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).

@@

\subsection{Contents}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).
